Compositional equivalences based on Open pNets

### 2020-02-12 2016-Weak-FH-Bisim/WeakBisim.tex
premiere tentative de conclusion

\section{Conclusion and Discussion}
\label{section:conclusion}

\TODO{LUDO: paragraphe d intro et de decription scientifique}

>>>>

\section{Conclusion and Discussion}
\label{section:conclusion}
 pNets (Parameterised Networks of Automata) is a formalism adapted to the representation of the behavior of a parallel or distributed systems. One  strength of pNets is their parameterized nature, making them adapted to the representation of systems of arbitrary size, and making the modelling of parameterized system possible. Parameters are also crucial to reason on interaction protocols that can address one entity inside an indexed set of processes.
This article focuses on open pNets that can represent process at the same time composition operators and
protocols synchronizing the actions of processes that can be plugged afterwards. Open
pNets can be defined as hierarchical composition of automata with holes and parameters. We
defined here a semantics for open pNets and a complete bisimulation theory for them.

The semantics of open pNets relies on the definition of open automata that are automata with holes and parameters, but no hierarchy. Open automata are somehow labelled transition systems with parameters and holes, a notion that is useful to define semantics, but makes less sense when modelling a system, compared to pNets. To be precise, it is on open automata that we define our bisimulation relations.

This articles defines a strong and a weak bisimulation principles that are adapted to parameterized systems and hierarchical composition. Our bisimulation principles handle pNets parameters in the sense that two states might be or not in relation depending on the value of parameters. Our strong  bisimulation is compositional by nature in the sense that bisimulation is maintained when composing processes. We also identified a simple and realistic condition on the semantics of non-observable actions that allows weak bisimulation to be also compositional. Overall we believe that this article paved the way for a solid theoretical foundation for compositional verification of parallel and distributed systems.
